Return on investment of private sector malaria control at a large sugar

### 2018-01-04 inst/rmd/paper.Rmd
formatting updates

---
title: Return on investment of private sector malaria control at a large sugar
  facility in Southern Mozambique
date: ''
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
# csl: journal-of-health-economics.csl
---

>>>>

---
title: Return on investment of private sector malaria control at a large sugar
  facility in Southern Mozambique
date: ''
output: 
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
    includes:
      in_header: preamble.sty
fig_width: 4
fig_height: 2.6
bibliography: bibliography.bib
csl: journal-of-health-economics.csl
---
